Can we use masked priming in an online setting?

### 2021-05-06 Manuscript_intro_method_results_AB.Rmd
Added Onedrive links

```{r exp1-blmm-table, echo=FALSE, as.is = TRUE}
# We fit the models in a separate file to make sure that knitting the manuscript doesn't take too long
load("blmm_exp1_rt_dist_full_ranef_5000.RData")
# model name is blmm_exp1_rt

@@

@@

```{r load_exp2_brms_data, echo=FALSE, as.is = TRUE}
# We fit the models in a separate file to make sure that knitting the manuscript doesn't take too long
load("blmm_exp2_rt_dist.RData")
# model name is blmm_exp2_rt

@@

>>>>

```{r exp1-blmm-table, echo=FALSE, as.is = TRUE}
# We fit the models in a separate file to make sure that knitting the manuscript doesn't take too long

load("blmm_exp1_rt_dist_full_ranef_5000.RData")
# This file does not fit on GitHub
# Download it at https://1drv.ms/u/s!ApE7JQmoH0baocARuxg21SFrS4riyg?e=8ZgbHA
# model name is blmm_exp1_rt_dist

@@

# This file does not fit on GitHub
# Download it at https://1drv.ms/u/s!ApE7JQmoH0baobQPat43HR3ixhuqww?e=VySttd

@@

```{r load_exp2_brms_data, echo=FALSE, as.is = TRUE}
# We fit the models in a separate file to make sure that knitting the manuscript doesn't take too long
load("blmm_exp2_rt_dist_full_ranef_5000.RData")
# this file doesn't fit on GitHub
# download it at https://1drv.ms/u/s!ApE7JQmoH0baocIO3qh2TNb_TlqvlA?e=q3vJml
# model name is blmm_exp2_rt

@@

# This file doesn't fit on GitHub
# Download it at https://1drv.ms/u/s!ApE7JQmoH0baobF4qRyXSfOymglf_g?e=0JGhre
